\chapter{本科期间的主要工作和成果}

\noindent 已接收论文
\begin{enumerate}
	\item \textbf{Liwenhan Xie}, James O'Donnell, Benjamin Bach, and Jean-Daniel Fekete. Interative Time-Series of Measures for Exploring Dynamic Networks. \emph{International Conference on Advanced Visual Interfaces}, Salerno, Italy, 2020.
	\item Can Liu, \textbf{Liwenhan Xie}, Yun Han, Datong Wei and Xiaoru Yuan. AutoCaption: An Approach to Generate Natural Language Description from Visualization Automatically. \emph{IEEE Pacific Visualization Symposium (Notes)}, Tianjin, China, 2020.
\end{enumerate}

\noindent 获奖作品/海报
\begin{enumerate}
	\item Shuai Chen, Sihang Li, \textbf{Liwenhan Xie}, Yi Zhong, Yun Han, and Xiaoru Yuan. EarthquakeAware: Visual Analytics for Understanding Human Impacts of Earthquakes from Social Media Data. \emph{IEEE Symposium on Visual Analytics Science and Technology (VAST Challenge)}, Vancouver, Canada, 2019. \textbf{Honorable Mention for Support for Analysis through Annotation and Context Award}.
	\item Can Liu, \textbf{Liwenhan Xie}, Yun Han, Datong Wei and Xiaoru Yuan. Auctomatic Caption Generation for SVG Charts. \emph{IEEE Pacific Visualization Symposium}, Bangkok, Thailand, 2019. \textbf{Honorable Mention for Best Poster Award}.
	\item Qi Ma, Chuangming Huang, \textbf{Liwenhan Xie}, Zhiyi Yin ,and Xiaoru Yuan.  Visual Analysis for Subgroups in a Dynamic Network. \emph{IEEE Symposium on Visual Analytics Science and Technology (VAST Challenge)}, Berlin, Germany, 2019. \textbf{Insights Generated Through the Use of a Custom Tool Award}.
	\item Lijing Lin, \textbf{Liwenhan Xie}, Zhuo Zhang, and Xiaoru Yuan. Visualizing Dynamic Networks of Long Sequences with Pixel Matrix Array. \emph{China Visualization and Visual Analytics Conference}, Sichuan, China, 2018. \textbf{Honorable Mention for Best Poster Award}.

\end{enumerate}
